Bioverse: Origins of Life

### 2023-11-03 src/tex/ms.tex
new plot showing spT distribution of different planets

>>>>

\begin{figure}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/inhabited_FGKM.pdf}
        \caption{Host stars of all transiting planets, \glspl{EEC}, and inhabited planets. In a sample of \var{N_nautilus} transiting planets, most \glspl{EEC} and all inhabited planets orbit M~dwarfs.}
        \label{fig:inhabited_FGKM}
    \end{centering}
\end{figure}

As shown in Figure~\ref{fig:inhabited_FGKM}, the majority of \glspl{EEC} and all inhabited planets orbit M~dwarfs.
